One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent flows

### 2020-10-02 submissions/initial_submission/manuscript.tex
initial submission

\begin{figure}
		\begin{tabular}{llll}
			\hspace{40pt}(a) & \hspace{100pt} (b) & \hspace{70pt} (c) & \hspace{50pt}(d) 
		\end{tabular}
	\begin{center}
		\begin{tabular}{c}
			\includegraphics[width=\textwidth]{../figures/tripletmap/tripmap.pdf} 
		\end{tabular}
	\end{center}
    \caption{Schematic diagram of a triplet map. From left to right: (a) simulation of a single ``eddy", a two-dimensional Kelvin-Helmholtz instability with a vertical white line-of-sight; (b) mixture fraction profile along the indicated line-of-sight before and after the eddy showing increased gradients and surface area; (c) a triplet map operates on a profile to produce a mapped profile with three copies, compressed and lined up, with the middle copy spatially inverted; (d) illustrative eddy event sizes and locations with corresponding temperature profile for a single ODT realization of a wall fire, adapted from \cite{Monson_2016}.}
\label{fig:tripletmap}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=\textwidth]{../figures/odt_flow_chart.pdf}
	\end{center}
	\caption{Structural outline of the ODT code, including its major class objects. For brevity, this diagram makes two simplifications. First, it assumes that diffusive advancement in the \texttt{micromixer} uses an explicit solution method; in practice, users specify either an explicit, semi-implicit, or Strang split method. Second, it implies that all of the eddy events sampled by the \texttt{eddy} object are applied to the domain; in reality, eddy events are filtered through several rejection tests (omitted from this figure for clarity) before acceptance and application to the domain.}
\label{fig:flowchart}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../figures/data_folder_structure.pdf} 
	\caption{Data folder structure and file locations. Boxes indicate folders and ovals indicate files. For a given simulation, \texttt{caseName} will be replaced with the case name specified in the run script. The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number. The number attached to \texttt{dmp} files indicates the output time step, or ``dump" time, of the data file. These correspond to the order of the time steps listed in \texttt{input.yaml}.}
\label{fig:data_folder_structure}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\begin{tabular}{ccc}
			(a) & (b) & (c) \\
			\includegraphics[width=1.7in]{../figures/cl_uvel_DLR_test_11.pdf} &
			\includegraphics[width=1.7in]{../figures/cl_mixf_DLR_test_11.pdf} &
			\includegraphics[width=1.7in]{../figures/cl_temp_DLR_test_11.pdf}
		\end{tabular}
	\end{center}
	\caption{DLR jet flame example case results: (a) mean axial velocity and RMS velocity along the centerline versus downstream location; (b) mean axial mixture fraction and RMS mixture fraction along the centerline versus downstream location; (c) mean axial temperature (K) and RMS temperature (K) along the centerline versus downstream location.}
\label{fig:dlr_example_results}
\end{figure}

@@

\bibliographystyle{elsarticle-num} 
\bibliography{references}

>>>>

\begin{figure}
		\begin{tabular}{llll}
			\hspace{40pt}(a) & \hspace{100pt} (b) & \hspace{70pt} (c) & \hspace{50pt}(d) 
		\end{tabular}
	\begin{center}
		\begin{tabular}{c}
            \includegraphics[width=\textwidth]{fig_tripmap.pdf} 
		\end{tabular}
	\end{center}
    \caption{Schematic diagram of a triplet map. From left to right: (a) simulation of a single ``eddy", a two-dimensional Kelvin-Helmholtz instability with a vertical white line-of-sight; (b) mixture fraction profile along the indicated line-of-sight before and after the eddy showing increased gradients and surface area; (c) a triplet map operates on a profile to produce a mapped profile with three copies, compressed and lined up, with the middle copy spatially inverted; (d) illustrative eddy event sizes and locations with corresponding temperature profile for a single ODT realization of a wall fire, adapted from \cite{Monson_2016}.}
\label{fig:tripletmap}
\end{figure}

@@

\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_odt_flow_chart.pdf}
	\end{center}
	\caption{Structural outline of the ODT code, including its major class objects. For brevity, this diagram makes two simplifications. First, it assumes that diffusive advancement in the \texttt{micromixer} uses an explicit solution method; in practice, users specify either an explicit, semi-implicit, or Strang split method. Second, it implies that all of the eddy events sampled by the \texttt{eddy} object are applied to the domain; in reality, eddy events are filtered through several rejection tests (omitted from this figure for clarity) before acceptance and application to the domain.}
\label{fig:flowchart}
\end{figure}

@@

\begin{figure}
	\centering
    \includegraphics[width=\textwidth]{fig_data_folder_structure.pdf} 
	\caption{Data folder structure and file locations. Boxes indicate folders and ovals indicate files. For a given simulation, \texttt{caseName} will be replaced with the case name specified in the run script. The number attached to \texttt{caseName} folder names and to \texttt{runtime} data files indicates the realization number. The number attached to \texttt{dmp} files indicates the output time step, or ``dump" time, of the data file. These correspond to the order of the time steps listed in \texttt{input.yaml}.}
\label{fig:data_folder_structure}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\begin{tabular}{ccc}
			(a) & (b) & (c) \\
            \includegraphics[width=1.7in]{fig_cl_uvel_DLR_test_11.pdf} &
            \includegraphics[width=1.7in]{fig_cl_mixf_DLR_test_11.pdf} &
            \includegraphics[width=1.7in]{fig_cl_temp_DLR_test_11.pdf}
		\end{tabular}
	\end{center}
	\caption{DLR jet flame example case results: (a) mean axial velocity and RMS velocity along the centerline versus downstream location; (b) mean axial mixture fraction and RMS mixture fraction along the centerline versus downstream location; (c) mean axial temperature (K) and RMS temperature (K) along the centerline versus downstream location.}
\label{fig:dlr_example_results}
\end{figure}

@@

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{Lignell_2015}
D.~O. Lignell, G.~C. Fredline, A.~D. Lewis, Comparison of one-dimensional
  turbulence and direct numerical simulations of soot formation and transport
  in a nonpremixed ethylene jet flame 35~(2) (2015) 1199--1206.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2014.05.046}
  {\path{doi:10.1016/j.proci.2014.05.046}}.

\bibitem{Abboud_2015}
A.~W. Abboud, C.~Schulz, T.~Saad, S.~T. Smith, D.~D. Harris, D.~O. Lignell, A
  numerical comparison of precipitating turbulent flows between large-eddy
  simulation and one-dimensional turbulence 61~(10) (2015) 3185--3197.
\newblock \href {http://dx.doi.org/10.1002/aic.14870}
  {\path{doi:10.1002/aic.14870}}.

\bibitem{Kerstein_1999}
A.~R. Kerstein, One-dimensional turbulence: model formulation and application
  to homogeneous turbulence, shear flows, and buoyant stratified flows 392
  (1999) 277--334.
\newblock \href {http://dx.doi.org/10.1017/S0022112099005376}
  {\path{doi:10.1017/S0022112099005376}}.

\bibitem{Kerstein_2000}
A.~R. Kerstein, T.~D. Dreeben, Prediction of turbulent free shear flow
  statistics using a simple stochastic model 12~(2) (2000) 418--424.
\newblock \href {http://dx.doi.org/10.1063/1.870319}
  {\path{doi:10.1063/1.870319}}.

\bibitem{Kerstein_2001}
A.~R. Kerstein, W.~T. Ashurst, S.~Wunsch, V.~Nilsen, One-dimensional
  turbulence: vector formulation and application to free shear flows 447 (2001)
  85--109.
\newblock \href {http://dx.doi.org/10.1017/S0022112001005778}
  {\path{doi:10.1017/S0022112001005778}}.

\bibitem{Echekki_2001}
T.~Echekki, A.~R. Kerstein, T.~D. Dreeben, J.-Y. Chen, `one-dimensional
  turbulence' simulation of turbulent jet diffusion flames: model formulation
  and illustrative applications 125~(3) (2001) 1083--1105.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00228-0}
  {\path{doi:10.1016/S0010-2180(01)00228-0}}.

\bibitem{Hewson_2001}
J.~C. Hewson, A.~R. Kerstein, Stochastic simulation of transport and chemical
  kinetics in turbulent
  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2 }flames 5~(4)
  (2001) 669--697.
\newblock \href {http://dx.doi.org/10.1088/1364-7830/5/4/309}
  {\path{doi:10.1088/1364-7830/5/4/309}}.

\bibitem{Hewson_2002}
J.~C. Hewson, A.~R. Kerstein, Local extinction and reignition in nonpremixed
  turbulent {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2} jet
  flames 174~(5-6) (2002) 35--66.
\newblock \href {http://dx.doi.org/10.1080/713713031}
  {\path{doi:10.1080/713713031}}.

\bibitem{Lignell_2012}
D.~O. Lignell, D.~S. Rappleye, One-dimensional-turbulence simulation of flame
  extinction and reignition in planar ethylene jet flames 159~(9) (2012)
  2930--2943.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2012.03.018}
  {\path{doi:10.1016/j.combustflame.2012.03.018}}.

\bibitem{Punati_2011}
N.~Punati, J.~C. Sutherland, A.~R. Kerstein, E.~R. Hawkes, J.~H. Chen, An
  evaluation of the one-dimensional turbulence model: comparison with direct
  numerical simulations of {CO}/{H}\textsubscript{2 }jets with extinction and
  reignition 33~(1) (2011) 1515--1522.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2010.06.127}
  {\path{doi:10.1016/j.proci.2010.06.127}}.

\bibitem{Abdelsamie_2017}
A.~Abdelsamie, D.~O. Lignell, D.~Th{\'e}venin, Comparison between {ODT} and
  {DNS} for ignition occurrence in turbulent premixed jet combustion:
  safety-relevant applications 231~(10) (2017) 1709--1735.
\newblock \href {http://dx.doi.org/10.1515/zpch-2016-0902}
  {\path{doi:10.1515/zpch-2016-0902}}.

\bibitem{Lignell_2017}
D.~O. Lignell, V.~B. Lansinger, A.~R. Kerstein, A cylindrical formulation of
  the one-dimensional turbulence ({ODT}) model for turbulent jet flames, in:
  AIChE Annual Meeting 2017, {American Institute of Chemical Engineers}, 2017.

\bibitem{Goshayeshi_2015}
B.~Goshayeshi, J.~C. Sutherland, Prediction of oxy-coal flame stand-off using
  high-fidelity thermochemical models and the one-dimensional turbulence model
  35~(3) (2015) 2829--2837.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2014.07.003}
  {\path{doi:10.1016/j.proci.2014.07.003}}.

\bibitem{Jozefik_2015}
Z.~Jozefik, A.~R. Kerstein, H.~Schmidt, S.~Lyra, H.~Kolla, J.~H. Chen,
  One-dimensional turbulence modeling of a turbulent counterflow flame with
  comparison to {DNS} 162~(8) (2015) 2999--3015.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2015.05.010}
  {\path{doi:10.1016/j.combustflame.2015.05.010}}.

\bibitem{Monson_2016}
E.~I. Monson, D.~O. Lignell, M.~A. Finney, C.~Werner, Z.~Jozefik, A.~R.
  Kerstein, R.~S. Hintze, Simulation of ethylene wall fires using the
  spatially-evolving one-dimensional turbulence model 52~(1) (2016) 167--196.
\newblock \href {http://dx.doi.org/10.1007/s10694-014-0441-2}
  {\path{doi:10.1007/s10694-014-0441-2}}.

\bibitem{Hewson_2006}
J.~C. Hewson, A.~J. Ricks, S.~R. Tieszen, A.~R. Kerstein, R.~O. Fox,
  Conditional-moment closure with differential diffusion for soot evolution in
  fire, in: Center for Turbulence Research, Proceedings of the Summer Program
  2006, {Stanford University}, 2006.

\bibitem{Hewson_2009}
J.~C. Hewson, A.~J. Ricks, S.~R. Tieszen, A.~R. Kerstein, R.~O. Fox, On the
  transport of soot relative to a flame: modeling differential diffusion for
  soot evolution in fire, in: H.~Bockhorn, A.~D'Anna, A.~F. Sarofim, H.~Wang
  (Eds.), Combustion Generated Fine Carbonaceous Particles, {KIT Scientific
  Publishing}, 2009, pp. 571--588.

\bibitem{Lignell_2015b}
D.~O. Lignell, J.~C. Hewson, One-dimensional turbulence simulation: overview
  and application to soot formation in nonpremixed flames, in: SIAM Conference
  on Computational Science and Engineering, 2015.

\bibitem{Ricks_2010}
A.~J. Ricks, J.~C. Hewson, A.~R. Kerstein, J.~P. Gore, S.~R. Tieszen, W.~T.
  Ashurst, A spatially developing one-dimensional turbulence ({ODT}) study of
  soot and enthalpy evolution in meter-scale buoyant turbulent flames 182~(1)
  (2010) 60--101.
\newblock \href {http://dx.doi.org/10.1080/00102200903297003}
  {\path{doi:10.1080/00102200903297003}}.

\bibitem{Sun_2017}
G.~Sun, J.~C. Hewson, D.~O. Lignell, Evaluation of stochastic particle
  dispersion modeling in turbulent round jets 89 (2017) 108--122.
\newblock \href {http://dx.doi.org/10.1016/j.ijmultiphaseflow.2016.10.005}
  {\path{doi:10.1016/j.ijmultiphaseflow.2016.10.005}}.

\bibitem{Schmidt_2009}
J.~R. Schmidt, J.~O.~L. Wendt, A.~R. Kerstein, Non-equilibrium wall deposition
  of inertial particles in turbulent flow 137~(2) (2009) 233--257.
\newblock \href {http://dx.doi.org/10.1007/s10955-009-9844-8}
  {\path{doi:10.1007/s10955-009-9844-8}}.

\bibitem{Sun_2014}
G.~Sun, D.~O. Lignell, J.~C. Hewson, C.~R. Gin, Particle dispersion in
  homogeneous turbulence using the one-dimensional turbulence model 26~(10)
  (2014) 103301.
\newblock \href {http://dx.doi.org/10.1063/1.4896555}
  {\path{doi:10.1063/1.4896555}}.

\bibitem{Fistler_2017}
M.~Fistler, D.~O. Lignell, A.~R. Kerstein, M.~Oevermann, Numerical studies of
  turbulent particle-laden jets using spatial approach of one-dimensional
  turbulence, in: ILASS-Europe 28th Conference on Liquid Atomization and Spray
  Systems, 2017.

\bibitem{Cao_2008}
S.~Cao, T.~Echekki, A low-dimensional stochastic closure model for combustion
  large-eddy simulation 9.
\newblock \href {http://dx.doi.org/10.1080/14685240701790714}
  {\path{doi:10.1080/14685240701790714}}.

\bibitem{Schmidt_2003}
R.~C. Schmidt, A.~R. Kerstein, S.~Wunsch, V.~Nilsen, Near-wall {LES} closure
  based on one-dimensional turbulence modeling 186~(1) (2003) 317--355.
\newblock \href {http://dx.doi.org/10.1016/S0021-9991(03)00071-8}
  {\path{doi:10.1016/S0021-9991(03)00071-8}}.

\bibitem{Schmidt_2010}
R.~C. Schmidt, A.~R. Kerstein, R.~McDermott, {ODTLES}: A multi-scale model for
  3{D} turbulent flow based on one-dimensional turbulence modeling 199~(13-16)
  (2010) 865--880.
\newblock \href {http://dx.doi.org/10.1016/j.cma.2008.05.028}
  {\path{doi:10.1016/j.cma.2008.05.028}}.

\bibitem{GonzalezJuez_2011}
E.~Gonzalez-Juez, A.~R. Kerstein, D.~O. Lignell, Fluxes across double-diffusive
  interfaces: a one-dimensional-turbulence study 677 (2011) 218--254.
\newblock \href {http://dx.doi.org/10.1017/jfm.2011.78}
  {\path{doi:10.1017/jfm.2011.78}}.

\bibitem{GonzalezJuez_2013}
E.~Gonzalez-Juez, A.~R. Kerstein, D.~O. Lignell, Reactive {R}ayleigh--{T}aylor
  turbulent mixing: a one-dimensional-turbulence study 107~(5) (2013) 506--525.
\newblock \href {http://dx.doi.org/10.1080/03091929.2012.736504}
  {\path{doi:10.1080/03091929.2012.736504}}.

\bibitem{Wunsch_2001}
S.~Wunsch, A.~R. Kerstein, A model for layer formation in stably stratified
  turbulence 13~(3) (2001) 702--712.
\newblock \href {http://dx.doi.org/10.1063/1.1344182}
  {\path{doi:10.1063/1.1344182}}.

\bibitem{Lignell_2018}
D.~O. Lignell, V.~B. Lansinger, J.~Medina, M.~Klein, A.~R. Kerstein,
  H.~Schmidt, M.~Fistler, M.~Oevermann, One-dimensional turbulence modeling for
  cylindrical and spherical flows: model formulation and application 32~(4)
  (2018) 495--520.
\newblock \href {http://dx.doi.org/10.1007/s00162-018-0465-1}
  {\path{doi:10.1007/s00162-018-0465-1}}.

\bibitem{Klein_2018}
M.~Klein, D.~O. Lignell, H.~Schmidt, Map-based modeling of turbulent
  convection: application of the one-dimensional turbulence model to planar and
  spherical geometries, in: International Conference on Rayleigh-Benard
  Turbulence, 2018.

\bibitem{Klein_2019}
M.~Klein, D.~O. Lignell, H.~Schmidt, Stochastic modeling of temperature and
  velocity statistics in spherical-shell convection, in: EGU Conference on
  Recent developments in Geophysical Fluid Dynamics, 2019.

\bibitem{Ashurst_2005}
W.~T. Ashurst, A.~R. Kerstein, One-dimensional turbulence: variable-density
  formulation and application to mixing layers 17~(2).
\newblock \href {http://dx.doi.org/10.1063/1.1847413}
  {\path{doi:10.1063/1.1847413}}.

\bibitem{Lignell_2013}
D.~O. Lignell, A.~R. Kerstein, G.~Sun, E.~I. Monson, Mesh adaption for
  efficient multiscale implementation of one-dimensional turbulence 27~(3-4)
  (2013) 273--295.
\newblock \href {http://dx.doi.org/10.1007/s00162-012-0267-9}
  {\path{doi:10.1007/s00162-012-0267-9}}.

\bibitem{Cengel_2010}
Y.~A. {\c{C}}engel, J.~M. Cimbala, Fluid Mechanics, 2nd Edition, {\c{C}}engel
  series in engineering thermal-fluid sciences, {McGraw-Hill Higher Education},
  2010.

\bibitem{Beder_2008}
J.~Beder, \href{https://github.com/jbeder/yaml-cpp/}{yaml-cpp v0.6.3} (2008).
\newline\urlprefix\url{https://github.com/jbeder/yaml-cpp/}

\bibitem{Strang_1968}
G.~Strang, On the construction and comparison of difference schemes 5~(3)
  (1968) 506--517.
\newblock \href {http://dx.doi.org/10.1137/0705041}
  {\path{doi:10.1137/0705041}}.

\bibitem{Hindmarsh_2020}
A.~C. Hindmarsh, R.~Serban, D.~R. Reynolds,
  \href{https://computing.llnl.gov/projects/sundials/cvode}{{CVODE}},
  https://computing.llnl.gov/sites/default/files/public/cv{\_}guide.pdf (2020).
\newline\urlprefix\url{https://computing.llnl.gov/projects/sundials/cvode}

\bibitem{Goodwin_2018}
D.~G. Goodwin, R.~L. Speth, H.~K. Moffat, B.~W. Weber,
  \href{https://cantera.org/}{Cantera} (2018).
\newblock \href {http://dx.doi.org/10.5281/zenodo.1174508}
  {\path{doi:10.5281/zenodo.1174508}}.
\newline\urlprefix\url{https://cantera.org/}

\bibitem{vanHeesch_2018}
D.~{van Heesch}, \href{https://www.doxygen.nl/}{Doxygen} (2018).
\newline\urlprefix\url{https://www.doxygen.nl/}

\bibitem{Yoo_2003}
A.~B. Yoo, M.~A. Jette, M.~Grondona, Slurm: simple linux utility for resource
  management, in: D.~G. Feitelson, L.~Rudolph, U.~Schwiegelshohn (Eds.), Job
  Scheduling Strategies For Parallel Processing, Vol. 2862 of Lecture notes in
  computer science, 0302-9743, Springer, 2003, pp. 44--60.
\newblock \href {http://dx.doi.org/10.1007/10968987-3}
  {\path{doi:10.1007/10968987-3}}.

\bibitem{Meier_2000}
W.~Meier, R.~S. Barlow, Y.-L. Chen, J.-Y. Chen,
  \href{https://tnfworkshop.org/data-archives/simplejet/dlrflames/}{Raman/{R}ayleigh/{LIF}
  measurements in a turbulent
  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2 }jet diffusion
  flame: experimental techniques and turbulence--chemistry interaction} 123~(3)
  (2000) 326--343.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(00)00171-1}
  {\path{doi:10.1016/S0010-2180(00)00171-1}}.
\newline\urlprefix\url{https://tnfworkshop.org/data-archives/simplejet/dlrflames/}

\bibitem{Pitsch_2000}
H.~Pitsch, Unsteady flamelet modeling of differential diffusion in turbulent
  jet diffusion flames 123~(3) (2000) 358--374.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(00)00135-8}
  {\path{doi:10.1016/S0010-2180(00)00135-8}}.

\bibitem{Lindstedt_2005}
R.~P. Lindstedt, H.~Ozarovsky, Joint scalar transported {PDF} modeling of
  nonpiloted turbulent diffusion flames 143~(4) (2005) 471--490.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2005.08.030}
  {\path{doi:10.1016/j.combustflame.2005.08.030}}.

\bibitem{Wang_2011}
H.~Wang, S.~B. Pope, Large eddy simulation/probability density function
  modeling of a turbulent
  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2} jet flame
  33~(1) (2011) 1319--1330.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2010.08.004}
  {\path{doi:10.1016/j.proci.2010.08.004}}.

\bibitem{Fairweather_2004}
M.~Fairweather, R.~M. Woolley, First-order conditional moment closure modeling
  of turbulent, nonpremixed methane flames 138~(1-2) (2004) 3--19.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2004.03.001}
  {\path{doi:10.1016/j.combustflame.2004.03.001}}.

\bibitem{Lee_2008}
K.~W. Lee, D.~H. Choi, Prediction of {NO} in turbulent diffusion flames using
  eulerian particle flamelet model 12~(5) (2008) 905--927.
\newblock \href {http://dx.doi.org/10.1080/13647830802094351}
  {\path{doi:10.1080/13647830802094351}}.

\bibitem{Lee_2009}
K.~W. Lee, D.~H. Choi, Analysis of {NO} formation in high temperature diluted
  air combustion in a coaxial jet flame using an unsteady flamelet model
  52~(5-6) (2009) 1412--1420.
\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2008.08.015}
  {\path{doi:10.1016/j.ijheatmasstransfer.2008.08.015}}.

\end{thebibliography}
